Towards a Machine Learning approach for Aggregate Computing

### 2021-11-26 paper-2021-woa-ac-ml.tex
minor on intro (w.r.t => w.r.t.)

In this direction, Aggregate Computing~\cite{DBLP:journals/computer/BealPV15}(AC) is an innovative paradigm, according to which
 developers can express collective self-organising behaviours through a functional program specification.
%
Indeed, an aggregate program (i.e. a program written with AC) consists of the manipulation of \textit{computational fields}, a distributed
 data structure where each point in the spacetime is associated with the result of a computation
 performed by a node.
%
%These operations are defined in \textit{field-calculus}~\cite{DBLP:conf/coordination/AudritoBDV18} --- the root of Aggregate Computing. 
% This calculus describes a set of minimal constructs to express any spatiotemporal computation.

AC captures common abstractions for collective behaviour specification. 
 These abstractions are encapsulated in so-called ``building blocks'' through which various
 applications have been built 
 (e.g., for swarm robotics and crowds engineering~\cite{DBLP:journals/eaai/CasadeiVAPD21}).
However, building block synthesis concerns different stuff not only related to the behaviour itself
 but also to the "ensemble" specifications. 
 For instance, it is quite difficult to craft building blocks
 that easily adapt w.r.t the node movements rapidity.

>>>>

In this direction, Aggregate Computing (AC)~\cite{DBLP:journals/computer/BealPV15} is an innovative paradigm, according to which
 developers can express collective self-organising behaviours through a functional program specification.
%
Indeed, an aggregate program (i.e. a program written with AC) consists of the manipulation of \textit{computational fields}, a distributed
 data structure where each point in the spacetime is associated with the result of a computation
 performed by a node.
%
%These operations are defined in \textit{field-calculus}~\cite{DBLP:conf/coordination/AudritoBDV18} --- the root of Aggregate Computing. 
% This calculus describes a set of minimal constructs to express any spatiotemporal computation.

AC captures common abstractions for collective behaviour specification. 
 These abstractions are encapsulated in so-called ``building blocks'' through which various
 applications have been built 
 (e.g., for swarm robotics and crowds engineering~\cite{DBLP:journals/eaai/CasadeiVAPD21}).
However, building block synthesis concerns different stuff not only related to the behaviour itself
 but also to the "ensemble" specifications. 
 For instance, it is quite difficult to craft building blocks
 that easily adapt w.r.t. the node movements rapidity.
